\Title

### 2016-10-06 manuscript/manuscript.tex
Add sentence to conclusion about figshare repo
Thank PhD commity for feedback
Fixes #38

@@

We are indebted to the developers and maintainers of the open-source
software without which this work would not have been possible.
We thank Dr. Marcelo Assumpção for providing the seismological Moho depth
estimates,
Editor Dr. Gary Egbert and two anonymous reviewers for their thoughtful
comments that helped improve this work.
L. Uieda was supported by a scholarship from
Coordenação de Aperfeiçoamento de Pessoal de Nível Superior
(CAPES).
V.C.F. Barbosa was supported by a fellowship from
Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq).

>>>>

Our gravity-derived Moho model for South America
can be downloaded from the online repository 
\url{http://dx.doi.org/10.6084/m9.figshare.3987267}.

@@

We are indebted to the developers and maintainers of the open-source
software without which this work would not have been possible.
We thank 
Marcelo Assumpção for providing the seismological Moho depth estimates,
Naomi Ussami, Julio C. S. O. Lyrio, Cosme F. P. Neto, and Daniel R. Franco
for their constructive feedback,
and Editor Dr. Gary Egbert and two anonymous reviewers for their thoughtful
comments that helped improve this work.
L. Uieda was supported by a scholarship from
Coordenação de Aperfeiçoamento de Pessoal de Nível Superior
(CAPES).
V.C.F. Barbosa was supported by a fellowship from
Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq).
